---
title: "Untitled"
author: "ShivaniR"
date: "11/3/2020"
output:
  pdf_document: default
  html_document: default
---
## PROBLEM STATEMENT
### From the given ‘Iris’ dataset, predict the optimum number of clusters and represent it visually.
### Assumption:To not take species colomn to form clusters and then use it to check our model performance

```{r}
library(ggplot2)
```

## DATA

```{r}
df <- iris
head(iris)

```
## EXPLORATORY DATA ANALYSIS

```{r}
ggplot(iris,aes(x = Sepal.Length, y = Sepal.Width, col= Species)) + geom_point()
ggplot(iris,aes(x = Petal.Length, y = Petal.Width, col= Species)) + geom_point()
```

### When Versicolor and Virginica Species is taken into consideration,noise is observed.It is also observed that the teo paarameters ,Petal.length and Petal.width seperate out Setosa species with very high confidence,hence aking it easy to be clustered.

## K Means clustering

```{r}
set.seed(101)
irisCluster <- kmeans(df[,1:4], center=3, nstart=20)
irisCluster
table(irisCluster$cluster, df$Species)
library(cluster)
```

## Optimimum number of clusters (Elbow method)

```{r}
tot.withinss <- vector(mode="character", length=10)
for (i in 1:10){
  irisCluster <- kmeans(df[,1:4], center=i, nstart=20)
  tot.withinss[i] <- irisCluster$tot.withinss
}
plot(1:10, tot.withinss, type="b", pch=19)
fitK = kmeans(df[,1:4], 3)
str(fitK)
plot(iris,col = fitK$cluster)
table(Predicted=fitK$cluster,Actual =iris$Species)
```
### Therefore ,the optimal number of clusters is 3.

## CLUSTER PLOT

```{r}
clusplot(iris, irisCluster$cluster, color=T, shade=T, labels=0, lines=0)
tot.withinss <- vector(mode="character", length=10)
for (i in 1:10){
  irisCluster <- kmeans(df[,1:4], center =i, nstart=20)
  tot.withinss[i] <- irisCluster$tot.withinss
}
```
### Therefore, 3 clusters are formed with varying sepal length and sepal width.
### The setosa cluster is perfectly explained, however virginica and versicolor have a little noise between their clusters,exact no of centres is obtained using Elbow method above.  

                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                        
                       